### 2019-03-10 papers/journal/encoding.tex
added the synthesis text for 6.3 Synthesis encoding

\subsection{Synthesis of VTS}
%In this section, we will present our synthesis method for
%the synthesis problems.

>>>>

\subsection{Synthesis of VTS}
In this section, we will present our synthesis method for
the synthesis problems.
%
We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.
